Storm surge modelling in the Strait of Georgia

### 2014-10-14 RoughWork/manuscript.tex
Edited caption of table

\begin{table}[h]
\centering 
\begin{tabular}{|l |c c c c c | c c c c c|} 
\hline 
& \multicolumn{5}{|c|}{Water Level ($\eta$)}        & \multicolumn{5}{|c|}{Residual ($\delta$)} \\ 
\hline 
Location       & $\bar{e}$ (cm) & $\bar{\eta_{o}}$ (m) & $\bar{\eta_{m}}$ (m) & $\gamma^2$ & $WS$   & $\bar{e}$ (cm) & $\bar{\delta_{o}}$ (m) & $\bar{\delta_{m}}$ (m) & $\gamma^2$ & $WS$ \\
\hline 
Point Atkinson & 10.5           & 3.46                 & 3.54                 &   0.012    & 0.994  & 6.2            &  0.273                 & 0.309                  & 0.065     & 0.979     \\
Victoria       &  8.6           & 2.18                 & 2.19                 &   0.032    & 0.992  & 6.1            &  0.235                 & 0.278                  & 0.085     & 0.970     \\
Patricia Bay   &  9.1           & 2.60                 & 2.64                 &   0.024    & 0.992  & 6.9            &  0.223                 & 0.278                  & 0.070     & 0.969     \\
Campbell River & 13.1           & 3.20                 & 3.21                 &   0.041    & 0.990  & 5.8            &  0.303                 & 0.300                  & 0.079     & 0.961     \\
\hline 
\end{tabular}
\caption{Evaluation of model performance for the Feb 2006 simulation. Mean absoulte error ($\bar{e}$), $\gamma^2$, and the Willmott skill score ($WS$) are provided for water level predictions ($\eta$) and resdiuals ($\delta$) during the period displayed in Figure \ref{fig:feb2006}.}
\label{tab:feb2006stat} 
\end{table} 
%anything else to include? statistics calculated in Feb 2006 -paper prodcution.ipynb and saved in statisitcs_feb2006.csv 
%mean of model and mean of observations?

>>>>

\begin{table}[h]
\centering 
\begin{tabular}{|l |c c c c c | c c c c c|} 
\hline 
& \multicolumn{5}{|c|}{Water Level ($\eta$)}        & \multicolumn{5}{|c|}{Residual ($\delta$)} \\ 
\hline 
Location       & $\bar{e}$ (cm) & $\bar{\eta_{o}}$ (m) & $\bar{\eta_{m}}$ (m) & $\gamma^2$ & $WS$   & $\bar{e}$ (cm) & $\bar{\delta_{o}}$ (m) & $\bar{\delta_{m}}$ (m) & $\gamma^2$ & $WS$ \\
\hline 
Point Atkinson & 10.5           & 3.46                 & 3.54                 &   0.012    & 0.994  & 6.2            &  0.273                 & 0.309                  & 0.065     & 0.979     \\
Victoria       &  8.6           & 2.18                 & 2.19                 &   0.032    & 0.992  & 6.1            &  0.235                 & 0.278                  & 0.085     & 0.970     \\
Patricia Bay   &  9.1           & 2.60                 & 2.64                 &   0.024    & 0.992  & 6.9            &  0.223                 & 0.278                  & 0.070     & 0.969     \\
Campbell River & 13.1           & 3.20                 & 3.21                 &   0.041    & 0.990  & 5.8            &  0.303                 & 0.300                  & 0.079     & 0.961     \\
\hline 
\end{tabular}
\caption{Evaluation of model performance for the Feb 2006 simulation. Mean absolute error ($\bar{e}$), observed mean (subscript o), modelled mean (subscript m), $\gamma^2$, and the Willmott skill score ($WS$) are provided for water level predictions ($\eta$) and resdiuals ($\delta$) during the period displayed in Figure \ref{fig:feb2006}.}
\label{tab:feb2006stat} 
\end{table} 
%anything else to include? statistics calculated in Feb 2006 -paper prodcution.ipynb and saved in statisitcs_feb2006.csv 
%mean of model and mean of observations?
